Compararison of analytical and artificial neural network models in predicting hot deformation behavior of AISI P20 and interpolation-extrapolation capacity validation

### 2022-10-18 Article.tex
Correction of two additional paragraphs in the Introduction

\OP{You must add here two paragraphs concerning a brief introduction to the Hansel-Spittel and the PTM models.}

>>>>

Users of the Forge software make extensive use of the model developed by Hansel and Spittel \cite{Hensel-1978}, commonly referred to as the HS model, which is a thermo-visco-plastic model whose formulation is based on a product of functions dependent on the three physical variables.  Unlike the JC model, this formulation is based on parameters that are determined simultaneously. This model is simple to use and has $8$ parameters that are easy to determine. The limitation of this model is its loss of accuracy in some cases when the $8$ parameters are defined. This is why many works often limit its identification to only $5$ or $6$ parameters. This has been verified in our study where the smallest error of the model is obtained with only $5$ parameters identified.

The fixed and limited number of parameters imposed by each analytical model as presented above has both advantages and disadvantages. These models have few parameters and are therefore easy to identify, but when these models have to be applied to a material different from the one for which they were initially developed they lose their performance as in the case of the HS model. To try to solve this problem, Tize Mha \eal \cite{TizeMha-2022} has proposed a formulation where the number of parameters is not known in advance. The idea is to make the formulation of an analytical model flexible so that it can be adapted to many materials. This formulation is based on the MZA model and polynomial functions of undefined order are used in the identification phase.
